Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-11 paper-ieee-trans.tex
added reference
changed title

\begin{document}
\title{Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena}

@@

Throughout the years, major developments have been focused on providing new
functionalities, while in the early days the adoption of software engineering procedures have had a higher priority.
The released software was less tested, causing a higher rate of
rollbacks and patches applied to production systems, compared to the software developed and maintained in the current projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised, affecting
negatively their exploitation by the scientific communities.
% Comments
%P1 C2 L24: Was this realisation imposed "from above" e.g. by coordinated EC/ERC oversight, or was it "emergent" from the demands of the independent scientific communities?
Therefore, it has become clear the need for a better balance between the addition of new features
and the reliability of the released software. Consequently, incoming projects progressively
devoted a substantial part of the software lifecycle to the improvement of the quality of the
software being delivered. At this point, evolving software engineering practices have been considered
so far and gradually adopted to define and implement quality procedures, the organization of
cross--functional teams and deployment of pilot testbeds.

>>>>

\begin{document}
\title{Evolution of Processes in Delivering Reliable Software in the European Scientific Arena}

@@

Throughout the years, major developments have been focused on providing new
functionalities, while in the early days the adoption of software engineering procedures have had a higher priority.
The released software was less tested, causing a higher rate of
rollbacks and patches applied to production systems, compared to the software developed and maintained in the current projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised, affecting
negatively their exploitation by the scientific communities \cite{aiftimiei}.
% Comments
%P1 C2 L24: Was this realisation imposed "from above" e.g. by coordinated EC/ERC oversight, or was it "emergent" from the demands of the independent scientific communities?
Therefore, it has become clear the need for a better balance between the addition of new features
and the reliability of the released software. Consequently, incoming projects progressively
devoted a substantial part of the software lifecycle to the improvement of the quality of the
software being delivered. At this point, evolving software engineering practices have been considered
so far and gradually adopted to define and implement quality procedures, the organization of
cross--functional teams and deployment of pilot testbeds.
